Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-02-17 Grassmannian_cells.tex
Hopefully addressed the comment.
Theorem 4.16 edits (mostly done)

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfI}{\mathbf{I}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\ui}{{\underline i}}
\newcommand{\uj}{{\underline j}}
\newcommand\udim{{\underline{\dim}\, }}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Ind}{\mathrm{Ind}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\rk}{\mathrm{rk}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\Att}{\operatorname{Att}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\xonto}[1]{\xrightarrow{#1}\!\!\!\!\!\to}
\newcommand{\ses}[3]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar[r] & #3 \ar[r] & 0}}
\newcommand{\sesm}[4]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar^{#4}[r] & #3 \ar[r] & 0}}
%\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\newcommand{\supp}{\operatorname{supp}}
\setcounter{MaxMatrixCols}{20}
\newcommand{\vs}{\vspace{0.2cm}}
\hyphenation{endo-functors}

@@

The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering.
\begin{definition}
  For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
  A sequence of subsets $\bfI=(I_0,I_1,\ldots,I_k)$, $k\ge1$, in $\{1,\ldots,n\}$ is \emph{admissible} if the following hold:
  \begin{enumerate}
    \item $|I_0|=n-1$ and $|I_l|=n-2$ for $1\le l\le k-1$;
    \item the sets $I'_l$ defined recursively by $I'_0=I_0$ and $I'_{l+1}:=(I'_l)^c\cup I_{l+1}$ for $0\le l\le k$ satisfy $(I'_l)^c\cap I_{l+1}=\varnothing$ for $0\le l\le k$.
  \end{enumerate}
  Here we take $I_{k+1}=\varnothing$ so that there is no condition imposed on the set $I_k$.

  Given an admissible sequence $\bfI$, define a new admissible sequence $\delta\bfI=(I'_1,I_2,\ldots,I_k)$, where we set $\delta(I_0)=(I'_1)$.
\end{definition}

@@

By Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
\[\sesm{\bigoplus_{i\in I\setminus J}\tilde P_{m,i}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}{\pi_{m+1}^{J,I}}.\]
For any sequence of proper subsets $K\subsetneq J\subsetneq I\subsetneq\{1,\ldots,n\}$, the quotient maps satisfy $\pi_{m+1}^{K,I}=\pi_{m+1}^{J,I}\circ\pi_{m+1}^{K,J}$ and $\pi_{m+1}^I=\pi_{m+1}^{J,I}\circ\pi_{m+1}^J$.
For $w\in W_n$, we write $\pi_{m+1,w}^{I,J}:\tilde P_{m+1,w}^I\to\tilde P_{m+1,w}^J$ for the translated morphism with similar notation for truncated preprojectives $\tilde P_{m+1-k,\ui}^I$ for $\ui\in A_1^{(k)}$ and $I\subsetneq\{1,\ldots,n\}$.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge3$, the following hold:
  \begin{enumerate}
    \item For $I\subsetneq\{1,\ldots,n\}$ with $|I|=n-1$ and $I^c=\{j\}$, we have an isomorphism 
      \[\tilde P_{m+1}^I\cong\tilde P_{m,j}^{I^c}=\tilde P_{m,j}/\tilde P_{m-1,(j,j)}.\]
    \item Consider an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and write $(I'_l)^c=\{i_l\}=:J_l$ for $0\le l\le k-1$.
      For $\ui=(i_0,\ldots,i_{k-1})$, there exists a commutative diagram:
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C70pt{\tilde P_{m+1} \ar^(.4){\pi_{m+1}^{I_0}}[d] & \ar[l] \tilde P_{m,i_0} \ar_(.4){\pi_{m,i_0}^{J_0}}[dl]\ar^(.4){\pi_{m,i_0}^{I'_1}}[d] & \ar[l] \tilde P_{m-1,(i_0,i_1)} \ar_(.4){\pi_{m-1,(i_0,i_1)}^{J_1}\;}[dl]\ar^(.4){\pi_{m-1,(i_0,i_1)}^{I'_2}}[d] & \ar[l] \ar[dl] \cdots & \ar[l] \tilde P_{m+1-k,\ui} \ar_(.4){\pi_{m+1-k,\ui}^{J_{k-1}}\;}[dl]\ar^(.4){\pi_{m+1-k}^{I'_k}}[d]\\
        \tilde P_{m+1}^{I'_0}\ar^{\pi_{m,i_0}^{J_0,I'_1}}[r] & \tilde P_{m,i_0}^{I'_1}\ar^{\pi_{m-1,(i_0,i_1)}^{J_1,I'_2}}[r] & \tilde P_{m-1,(i_0,i_1)}^{I'_2}\ar^(.6){\pi_{m-2,(i_0,i_1,i_2)}^{J_2,I'_3}}[r] & \cdots\ar^{\pi_{m+1-k,\ui}^{J_{k-1},I'_k}}[r] & \tilde P_{m+1-k,\ui}^{I'_k}}
      \end{equation}
      where the composed map $\pi_{m+1}^\bfI:\tilde P_{m+1}\to\tilde P_{m+1-k,\ui}^{I'_k}$ is unique up to scaling and therefore we write
      \[\tilde P_{m+1}^\bfI:=\tilde P_{m+1-k,\ui}^{I'_k}.\]
      These truncated preprojective representations satisfy 
      \[\tilde P_{m+1}^\bfI=\tilde P_{m,i_0}^{\delta\bfI}=\cdots=\tilde P_{m+1-k,\ui}^{\delta^k\bfI}.\]
  \end{enumerate}
\end{lemma}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

@@

\subsection{Fibrations of Quiver Grassmannians}
\label{sec:fibrations}
Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
This induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,U\mapsto (U\cap M,(U+M)/M).\]
Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi_\tbfe$ satisfies $\Psi^{-1}_\tbfe(V,W)=\mathbb{A}^{\dim\Hom(W,M/V)}$.

@@

We will apply this result in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
Fix $m\ge1$.
For subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
\[\ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}\]
which induces a map between quiver Grassmannians as above:
\[\Psi_{m+1,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).\]
To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
Here we consider the short exact sequence 
\[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},\]
where $\tilde K_m=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
Then in the same way as above we obtain the map
\[\Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_m(I,j))\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).\]
\begin{proposition}
  \label{quotient}
  For $m\geq 2$ and a nonempty subset $I\subsetneq\{1,\ldots,n\}$.
  The following hold for any $j\in I$:
  \begin{enumerate}
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi_{m,I,j}(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
  \end{enumerate} 
\end{proposition}
\begin{proof}
  Any subrepresentation $U\subset\tilde P_{m,j}$ produces an exact sequence
  \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
  But note that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ being nonempty gives rise to a pushout diagram
  \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
  in which the bottom row is not split by Lemma~\ref{le:properties}.(4).
  This implies that the map 
  \[\Ext(\tilde P_{m+1}^I,U)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
  This argument can be reversed and thus (1) holds.

@@

Now we are able to state the following result concerning the fibers of $\Psi_{m+1,I,j}$:
\begin{proposition}
  \label{fibers}
  The following hold:
  \begin{enumerate}
    \item For $V\subsetneq\tilde P_{m+1}^I$ and $U\subseteq\tilde P_{m,j}$, we have $\Psi_{m+1,I,j}^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,j}/U\rangle}$.
    \item If $V=\tilde P_{m+1}^I$, the fiber $\Psi_{m+1,I,j}^{-1}(U,V)$ is not empty if and only if $\Phi_{m,I,j}(U)\neq(U,0)$.
      In this case, we have $\Psi_{m+1,I,j}^{-1}(U,V)=\AA^{\langle V,\tilde P_{m,j}/U\rangle}$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  By Lemma~\ref{le:subrep}, any subrepresentation $V\subsetneq\tilde P_{m+1}^I$ is preprojective.
  But the representation $\tilde P_{m,j}/U$ is not preprojective as it is a proper quotient of a preprojective representation unless $U=0$.
  Thus we have $\Ext(V,\tilde P_{m,j}/U)=0$. 
  If $U=0$, we have $\Ext(V,\tilde P_{m,j})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to a lift of some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_k)=0$ for $l\leq k+1$.

@@

\begin{theorem}
  \label{cellscover}
  For $m\geq 1$ and $I\subset\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition into affine spaces.
\end{theorem}
\begin{proof}

In order to prove the claim, we prove the following more general statement:\\

\noindent {\bf Claim.} Let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\geq 1$ be an arbitrary admissible sequence and $\underline{j_1}=(\uj,j_{1,l+1},\ldots,j_{1,n-1})\in I_{n-1}$. The quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ has a cell decomposition into affine spaces which is compatible with $\pi_{m,\uj}^{\bf j}$  in the following way: 
 Let $U\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ such that $\pi_m^{\bf j}(U)\neq 0.$
Then we have $\pi_{m,\uj}^{\bf j}(U')\neq 0$ for all $U'\in C_U$ where $C_U$ is the cell which contains $U$.
\vs

>>>>

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfI}{\mathbf{I}}
\newcommand{\bfJ}{\mathbf{J}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\ui}{{\underline i}}
\newcommand{\uj}{{\underline j}}
\newcommand\udim{{\underline{\dim}\, }}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Ind}{\mathrm{Ind}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\rk}{\mathrm{rk}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\Att}{\operatorname{Att}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\xonto}[1]{\xrightarrow{#1}\!\!\!\!\!\to}
\newcommand{\ses}[3]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar[r] & #3 \ar[r] & 0}}
\newcommand{\sesm}[4]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar^{#4}[r] & #3 \ar[r] & 0}}
%\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\newcommand{\supp}{\operatorname{supp}}
\setcounter{MaxMatrixCols}{20}
\newcommand{\vs}{\vspace{0.2cm}}
\hyphenation{endo-functors}

@@

The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering.
\begin{definition}
  For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
  A sequence of subsets $\bfI=(I_0,I_1,\ldots,I_k)$, $k\ge0$, in $\{1,\ldots,n\}$ is \emph{admissible} if the following hold:
  \begin{enumerate}
    \item if $k\ge1$, then $|I_0|=n-1$ and $|I_l|=n-2$ for $1\le l\le k-1$;
    \item the sets $I'_l$ defined recursively by $I'_0=I_0$ and $I'_{l+1}:=I_{l+1}\cup (I'_l)^c$ for $0\le l\le k$ satisfy $(I'_l)^c\cap I_{l+1}=\varnothing$ for $0\le l\le k$.
  \end{enumerate}
  Here we take $I_{k+1}=\varnothing$ so that there is no condition imposed on the set $(I'_k)^c$.
  Given an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k\ge1$, define a new admissible sequence $\delta\bfI=(I'_1,I_2,\ldots,I_k)$.
\end{definition}

@@

By Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
\[\sesm{\bigoplus_{i\in I\setminus J}\tilde P_{m,i}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}{\pi_{m+1}^{J,I}}.\]
For any sequence of proper subsets $K\subsetneq J\subsetneq I\subsetneq\{1,\ldots,n\}$, the quotient maps satisfy $\pi_{m+1}^{K,I}=\pi_{m+1}^{J,I}\circ\pi_{m+1}^{K,J}$ and $\pi_{m+1}^I=\pi_{m+1}^{J,I}\circ\pi_{m+1}^J$.
For $w\in W_n$, we write $\pi_{m+1,w}^{I,J}:\tilde P_{m+1,w}^I\to\tilde P_{m+1,w}^J$ for the translated morphism with similar notation for truncated preprojectives $\tilde P_{m+1-k,\ui}^I$ for $\ui\in A_1^{(k)}$ and $I\subsetneq\{1,\ldots,n\}$.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge3$, the following hold:
  \begin{enumerate}
    \item For $I\subsetneq\{1,\ldots,n\}$ with $|I|=n-1$ and $I^c=\{j\}$, we have an isomorphism 
      \[\tilde P_{m+1}^I\cong\tilde P_{m,j}^{I^c}=\tilde P_{m,j}/\tilde P_{m-1,(j,j)}.\]
    \item Consider an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $0<k<m$ and write $(I'_l)^c=\{i_l\}=:J_l$ for $0\le l\le k-1$.
      For $\ui=(i_0,\ldots,i_{k-1})$, there exists a commutative diagram:
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C70pt{\tilde P_{m+1} \ar^(.4){\pi_{m+1}^{I'_0}}[d] & \ar[l] \tilde P_{m,i_0} \ar_(.4){\pi_{m,i_0}^{J_0}}[dl]\ar^(.4){\pi_{m,i_0}^{I'_1}}[d] & \ar[l] \tilde P_{m-1,(i_0,i_1)} \ar_(.4){\pi_{m-1,(i_0,i_1)}^{J_1}\;}[dl]\ar^(.4){\pi_{m-1,(i_0,i_1)}^{I'_2}}[d] & \ar[l] \ar[dl] \cdots & \ar[l] \tilde P_{m+1-k,\ui} \ar_(.4){\pi_{m+1-k,\ui}^{J_{k-1}}\;}[dl]\ar^(.4){\pi_{m+1-k}^{I'_k}}[d]\\
        \tilde P_{m+1}^{I'_0}\ar^{\pi_{m,i_0}^{J_0,I'_1}}[r] & \tilde P_{m,i_0}^{I'_1}\ar^{\pi_{m-1,(i_0,i_1)}^{J_1,I'_2}}[r] & \tilde P_{m-1,(i_0,i_1)}^{I'_2}\ar^(.6){\pi_{m-2,(i_0,i_1,i_2)}^{J_2,I'_3}}[r] & \cdots\ar^{\pi_{m+1-k,\ui}^{J_{k-1},I'_k}}[r] & \tilde P_{m+1-k,\ui}^{I'_k}}
      \end{equation}
      where the composed map $\pi_{m+1}^\bfI:\tilde P_{m+1}\to\tilde P_{m+1-k,\ui}^{I'_k}$ is unique up to scaling and therefore we write
      \[\tilde P_{m+1}^\bfI:=\tilde P_{m+1-k,\ui}^{I'_k}.\]
      These truncated preprojective representations satisfy 
      \[\tilde P_{m+1}^\bfI=\tilde P_{m,i_0}^{\delta\bfI}=\cdots=\tilde P_{m+1-k,\ui}^{\delta^k\bfI}.\]
  \end{enumerate}
\end{lemma}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

@@

\subsection{Fibrations of Quiver Grassmannians}
\label{sec:fibrations}
Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
This induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
\[\Psi_\tbfe:\Gr_\tbfe(B)\to\bigsqcup_{\tbff+\tbfg=\tbfe}  \Gr_\tbff(M)\times \Gr_\tbfg(N),\,V\mapsto (V\cap M,(V+M)/M).\]
Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi_\tbfe$ satisfies $\Psi^{-1}_\tbfe(U,W)=\mathbb{A}^{\dim\Hom(W,M/U)}$.

@@

We will apply this result in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
Fix $m\ge1$.
For subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
\begin{equation}
  \label{eq:truncated ses}
  \ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}
\end{equation}
which induces a map between quiver Grassmannians as above:
\begin{equation}
  \label{eq:truncated CC}
  \Psi_{m+1,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
\end{equation}
To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
Here we consider the short exact sequence 
\[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},\]
where $\tilde K_m=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
Then in the same way as above we obtain the map
\begin{equation}
  \label{eq:truncated CC2}
  \Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_m(I,j))\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).
\end{equation}
\begin{proposition}
  \label{quotient}
  For $m\geq 2$ and a nonempty subset $I\subsetneq\{1,\ldots,n\}$.
  The following hold for any $j\in I$:
  \begin{enumerate}
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi_{m,I,j}(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
  \end{enumerate} 
\end{proposition}
\begin{proof}
  Any subrepresentation $U\subset\tilde P_{m,j}$ produces an exact sequence
  \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
  But note that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ being nonempty gives rise to a pushout diagram
  \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
  in which the bottom row is not split by Lemma~\ref{le:properties}.(4).
  This implies that the map 
  \[\Ext(\tilde P_{m+1}^I,U)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
  This argument can be reversed and thus (1) holds.

@@

Now we are able to state the following result concerning the fibers of $\Psi_{m+1,I,j}$:
\begin{proposition}
  \label{fibers}
  The following hold:
  \begin{enumerate}
    \item For $W\subsetneq\tilde P_{m+1}^I$ and $U\subseteq\tilde P_{m,j}$, we have $\Psi_{m+1,I,j}^{-1}(U,W)=\AA^{\langle W,\tilde P_{m,j}/U\rangle}$.
    \item If $W=\tilde P_{m+1}^I$, the fiber $\Psi_{m+1,I,j}^{-1}(U,W)$ is not empty if and only if $\Phi_{m,I,j}(U)\neq(U,0)$.
      In this case, we have $\Psi_{m+1,I,j}^{-1}(U,W)=\AA^{\langle W,\tilde P_{m,j}/U\rangle}$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  By Lemma~\ref{le:subrep}, any subrepresentation $V\subsetneq\tilde P_{m+1}^I$ is preprojective.
  But the representation $\tilde P_{m,j}/U$ is not preprojective as it is a proper quotient of a preprojective representation unless $U=0$.
  Thus we have $\Ext(W,\tilde P_{m,j}/U)=0$. 
  If $U=0$, we have $\Ext(W,\tilde P_{m,j})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to a lift of some $P_l$ with $l\leq m$ and, moreover, $\Ext(P_l,P_k)=0$ for $l\leq k+1$.

@@

\begin{theorem}
  \label{cellscover}
  For $m\geq 1$ and $I\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition into affine spaces.
\end{theorem}
\begin{proof}
  We work by induction on $m$.
  When $m=1$, the claim is trivial since all quiver Grassmannians are points in this case.
  We establish the result for $m\ge2$ by proving the following more general statement:\\

  \noindent{\bf Claim.}
  For any proper subset $J\subsetneq\{1,\ldots,n\}$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a decomposition into affine spaces with the following property:
  \begin{itemize}
    \item[($\dagger$)] For any admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and $J\subset I_0$ consider the unique map $\pi_{m+1}^{J,\bfI}:\tilde P_{m+1}^J\to\tilde P_{m+1}^\bfI$ from Lemma~\ref{le:truncated quotients}.
      For any $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\pi_{m+1}^{J,\bfI}(V)\neq 0$, we have $\pi_{m+1}^{J,\bfI}(V')\neq 0$ for all $V'\in C_V$, where $C_V$ is the affine cell which contains $V$.
  \end{itemize}
  \vs

  In what follows, we will freely use the notation from Lemma~\ref{le:truncated quotients}.
  We proceed by simultaneous induction on $m$ and reverse induction on $|J|$.
  Fix an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and $J\subset I_0$.

  To begin, we assume $|J|=n-1$ and thus $J=I_0$.
  This gives $\tilde P_{m+1}^J\cong\tilde P_{m,i_0}^{J_0}$ and so by induction on $m$ the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)=\Gr^{\tilde Q}_\tbfe(\tilde P_{m,i_0}^{J_0})$ admits a decomposition into affine spaces so that the compatibility condition ($\dagger$) holds for the unique map $\pi_{m,i_0}^{J_0,\delta\bfI}:\tilde P_{m,i_0}^{J_0}\to\tilde P_{m,i_0}^{\delta\bfI}$.
  But $\tilde P_{m,i_0}^{\delta\bfI}=\tilde P_{m+1}^\bfI$ so that $\pi_{m,i_0}^{J_0,\delta\bfI}$ coincides with the map $\pi_{m+1}^{J,\bfI}$ and thus the condition ($\dagger$) holds for the cell decomposition of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.

  Now suppose $|J|<n-1$.
  If $J=I_0$, then we must have $k=0$ and $\tilde P_{m+1}^J=\tilde P_{m+1}^\bfI$ so that the compatibility condition ($\dagger$) with the map $\pi_{m+1}^{J,\bfI}$ is vacuous.
  Thus we may assume $J\subsetneq I_0$.

  Choose any subset $I\subsetneq\{1,\ldots,n\}$ with $J\subset I$ and $|I\setminus J|=1$, say $I\setminus J=\{j\}$.
  This gives the short exact sequence \eqref{eq:truncated ses} inducing the maps $\Psi_{m+1,I,j}$ and $\Phi_{m,I,j}$ between quiver Grassmannians from \eqref{eq:truncated CC} and \eqref{eq:truncated CC2}.
  There are two cases to consider.
